\chapter{Symbols}
\label{app:symbols}

This appendix summarises the important symbols used throughout the dissertation.
For each symbol, a short description is provided as well as the reference to the
equation that makes use it. Symbols are divided according to the chapter in
which they were introduced and are ordered alphabetically.


\section{Chapter~\ref{chap:anns}: Artificial Neural Networks}
\label{sec:symbols:anns}

\todo[inline]{ref usage}
  
\begin{description}
    \item
    [\parbox{1cm}{$\alpha$}] Control parameter for leaky ReLU that controls non-zero gradients.

    \item
    [\parbox{1cm}{$\beta$}] Batch size.

    \item
    [\parbox{1cm}{$c$}] Index for classes.

    \item
    [\parbox{1cm}{$C$}] Total number of classes.

    \item
    [\parbox{1cm}{$E$}] Total number of epochs.

    \item
    [\parbox{1cm}{$\epsilon$}] Error value calculated from loss/cost function.

    \item
    [\parbox{1cm}{$f$}] The activation function implemented by the \ac{AN}.

    \item
    [\parbox{1cm}{$f_{AN}$}] The non-linear function represented by the \ac{AN}.

    \item
    [\parbox{1cm}{$\vec{h}$}] The vector representing the activations of the hidden units.

    \item
    [\parbox{1cm}{$h_j$}] The $j$-th hidden unit and thus its activation.

    \item
    [\parbox{1cm}{$i$}] Index for the input dimensions.

    \item
    [\parbox{1cm}{$I$}] Total number of dimensions on the input space.

    \item
    [\parbox{1cm}{$j$}] Index for the hidden layer.

    \item
    [\parbox{1cm}{$J$}] The total number of units in the hidden layer.

    \item
    [\parbox{1cm}{$k$}] Index for the output dimensions.

    \item
    [\parbox{1cm}{$K$}] The total number of dimensions in the output space.

    \item
    [\parbox{1cm}{$\lambda$}] Control parameter for the steepness of sigmoid and hyperbolic tangent activation functions.

    \item
    [\parbox{1cm}{$net$}] The net input signal.

    \item
    [\parbox{1cm}{$net'$}] The augmented net input signal which contains the bias term $\theta$.

    \item
    [\parbox{1cm}{$\mu_i$}] The mean over all input patterns at index $i$.

    \item
    [\parbox{1cm}{$p$}] Index used for patterns in the set of all training data.

    \item
    [\parbox{1cm}{$P$}] Total number of patterns in the training data.

    \item
    [\parbox{1cm}{$\omega_{min}$}] The lower bound of the range for random uniform sampling.

    \item
    [\parbox{1cm}{$\omega_{max}$}] The upper bound of the range for random uniform sampling.

    \item
    [\parbox{1cm}{$\mathbb{R}$}] The real number space.

    \item
    [\parbox{1cm}{$\sigma$}] The standard deviation.

    \item
    [\parbox{1cm}{$\sigma_i^2$}] Unit variance.

    \item
    [\parbox{1cm}{$T$}] The total number of dimensions in the target space.

    \item
    [\parbox{1cm}{$\theta$}] The bias or threshold term.

    \item
    [\parbox{1cm}{$\vec{v}$}] The vector of weights associated with the input.

    \item
    [\parbox{1cm}{$v_i$}] The $i$-th index of the weight vector associated with the input.

    \item
    [\parbox{1cm}{$v_{i,j}$}] The $i,j$-th index of the weight vector between the input and hidden layers.

    \item
    [\parbox{1cm}{$\vec{w}$}] The weight vector between the hidden and output layers.

    \item
    [\parbox{1cm}{$w_{j,k}$}] The $j,k$-th index of the weight vector between the hidden and output layers.

    \item
    [\parbox{1cm}{$\vec{x}$}] The input vector.

    \item
    [\parbox{1cm}{$\vec{x}_p$}] The input vector for pattern $p$.

    \item
    [\parbox{1cm}{$x_i$}] The $i$-th index of the input vector $\vec{x}$

    \item
    [\parbox{1cm}{$x_{i,p}$}] The $i$-th index of the input vector $\vec{x}$ for pattern $p$.

    \item
    [\parbox{1cm}{$x_{i,p}'$}] The pre-processed input at the $i$-th index of the input vector $\vec{x}$ for pattern $p$.

    \item
    [\parbox{1cm}{$x_{i_{min}}$}] The minimum value at the  $i$-th index of the input vector $\vec{x}$  for all patterns in $P$.

    \item
    [\parbox{1cm}{$x_{i_{max}}$}] The maximum value at the  $i$-th index of the input vector $\vec{x}$  for all patterns in $P$.

    \item
    [\parbox{1cm}{$\vec{y}$}] The output vector.

    \item
    [\parbox{1cm}{$\vec{y}_p$}] The output vector for pattern $p$.

    \item
    [\parbox{1cm}{$y_k$}] The $k$-th dimension of the output vector $\vec{y}$.

    \item
    [\parbox{1cm}{$y_{k}'$}] The post-processed output at the $k$-th dimension of the output vector $\vec{y}$.

    \item
    [\parbox{1cm}{$y_{k,p}$}] The $k$-th dimension of the output vector $\vec{y}$ for pattern $p$.

    \item
    [\parbox{1cm}{$y_{k,p}'$}] The post-processed output at the $k$-th dimension of the output vector $\vec{y}$ for pattern $p$.

    \item
    [\parbox{1cm}{$\hat{y}_{k,p}$}] The $k$-th dimension of the target output for pattern $p$. 
\end{description}

