\pagestyle{empty}
\begin{center}
    \Large
    \textbf{Acknowledgements}
\end{center}

\begin{quotation}
    \noindent
    ``I've made the most important discovery of my life. It's only in
    the mysterious equation of love that any logical reasons can be found. I'm
    only here tonight because of you. You are the only reason I am \ldots you are
    all my reasons.''
\end{quotation}
\begin{flushright}
    Prof. J.F. Nash, Jr.
\end{flushright}

\vspace{0.3cm}
\noindent
I would like to thank the following people, without whom this work would never
have been possible:

\begin{itemize}
    \item
    To my wife, Taylah. Thank you for always believing in me. You are all my
    reasons.

    \item
        To my daughter, Bean\'e. Thank you for giving life meaning.
        
    \item
        To my son, Aden. I can't wait to meet you!

    \item
        To my parents, Adr\'e and Engela. Thank you for making this possible.

    \item
    To my sister, Jeannie. Thank you for motivating me.

    \item
    To my supervisors, Dr.~A. Bosman, Dr.~C.W. Cleghorn and Prof.~A.P. Engelbrecht. Thank you
    for leading me.

    \item
    To my creator, God. Thank You \ldots for Everything!
\end{itemize}

\vspace{\fill}

\begin{center}
    This project was made possible by the National Research Foundation (NRF).\\
    Thank you for the opportunity.
\end{center}

\vspace{\fill}

\begin{center}
    Finally, this project would not have been possible if it were not for the generous hours and hours of computational time I was given on the Center for High Performance Computing (CHPC) Cluster at the Council for Scientific and Industrial Research (CSIR).
\end{center}

\newpage
